% !TEX TS-program = xelatex
% !TEX encoding = UTF-8 Unicode
% -*- coding: UTF-8; -*-
% vim: set fenc=utf-8

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% CV.tex
%% <https://github.com/zachscrivena/simple-resume-cv>
%% This is free and unencumbered software released into the
%% public domain; see <http://unlicense.org> for details.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% See "README.md" for instructions on compiling this document.

\documentclass[letterpaper,MMMyyyy,nonstopmode]{simpleresumecv}
% Class options:
% a4paper, letterpaper, nonstopmode, draftmode
% MMMyyyy, ddMMMyyyy, MMMMyyyy, ddMMMMyyyy, yyyyMMdd, yyyyMM, yyyy

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% PREAMBLE.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% CV Info (to be customized).
\newcommand{\CVAuthor}{Riley J. Mangan}
\newcommand{\CVTitle}{Riley J. Mangan Curriculum Vitae}
%\newcommand{\CVNote}{CV compiled on {\today}}
\newcommand{\CVWebpage}{http://www.vertgenlab.org}

% PDF settings and properties.
\hypersetup{
pdftitle={\CVTitle},
pdfauthor={\CVAuthor},
pdfsubject={\CVWebpage},
pdfcreator={XeLaTeX},
pdfproducer={},
pdfkeywords={},
unicode=true,
bookmarks=true,
bookmarksopen=true,
pdfstartview=FitH,
pdfpagelayout=OneColumn,
pdfpagemode=UseOutlines,
hidelinks,
breaklinks}

% Shorthand.
\newcommand{\Code}[1]{\mbox{\textbf{#1}}}
\newcommand{\CodeCommand}[1]{\mbox{\textbf{\textbackslash{#1}}}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% ACTUAL DOCUMENT.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%%%%%%%%%%%%%%%
% TITLE BLOCK %
%%%%%%%%%%%%%%%

\Title{\CVAuthor}

\begin{SubTitle}
%813 Louise Circle, Durham, North Carolina 27705
%\par
\href{mailto:riley.mangan@duke.edu}
{riley.mangan@duke.edu}
%\,\SubBulletSymbol\,
%\,(847)\,767-9690
\,\SubBulletSymbol\,
\href{\CVWebpage}
{\url{\CVWebpage}}
\end{SubTitle}

\begin{Body}

%%%%%%%%%%%%%%%
%% EDUCATION %%
%%%%%%%%%%%%%%%

\Section
{Education}
{Education}
{PDF:Education}

\Entry

{\textbf{Duke University}},
Durham, North Carolina \hfill
\DatestampYMD{2018}{8}{15} --Present

\Gap
\BulletItem
Ph.D. - 
\href{https://mgm.duke.edu/}
{Molecular Genetics and Microbiology}, In Progress

\begin{Detail}
\SubBulletItem
Graduate Program in Cell and Molecular Biology
\SubBulletItem
Cumulative GPA: 3.977 / 4.0
\SubBulletItem
\href{http://www.vertgenlab.org/}{Laboratory of Craig B. Lowe, Ph.D.}
\end{Detail}

\BigGap
\Entry
\href{https://www.davidson.edu/}
{\textbf{Davidson College}},
Davidson, North Carolina \hfill
\DatestampYMD{2012}{08}{15} --
\DatestampYMD{2016}{05}{15}

\Gap
\BulletItem
B.S. -
\href{https://www.davidson.edu/academic-departments/biology}
{Biology, \textit{Magna Cum Laude}}

\begin{Detail}
\SubBulletItem
Cumulative GPA: 3.79 / 4.0
\SubBulletItem
Major GPA: 3.91 / 4.0
\end{Detail}

%%%%%%%%%%%%%%%%%%%%%%%%%
%% RESEARCH EXPERIENCE %%
%%%%%%%%%%%%%%%%%%%%%%%%%



\Section
{Research Experience}
{Research Experience}
{PDF:ResearchExperience}


\Entry
\textbf{Duke University School of Medicine}, 
Durham, North Carolina \hfill
\DatestampYMD{2018}{08}{15} -- Present

\Gap
\BulletItem
Graduate Student, Laboratory of Craig B. Lowe, Ph.D. 

\begin{Detail}
\SubBulletItem
\textbf{\textit{Central Focus}}: My work combines interdisciplinary tools from computational genomics, neurodevelopment, and molecular evolution to investigate how human-specific gene regulatory innovation has led to human-unique disease susceptibility and the emergence of our unique cognitive capabilities.
\SubBulletItem
I have designed and implemented novel bioinformatic software to identify fast-evolving regions of the human genome and to identify the gene regulatory functions of these regions in the developing brain.
\SubBulletItem
I developed \textit{in vivo} STARR-seq, a high-throughput, single-cell, multiplex enhancer assay to quantify the cell type-specific enhancer activity of DNA sequences from extant and ancient vertebrate species in developing brain tissue.
\SubBulletItem
Co-developer of Gonomics, an open-source genomics software platform for the Go programming language.
\end{Detail}

\BigGap
\Entry
\href{https://dhvi.duke.edu/}
{\textbf{Duke Human Vaccine Institute}},
Durham, North Carolina \hfill
\DatestampYMD{2016}{05}{15} --
\DatestampYMD{2018}{07}{15}

\Gap
\BulletItem
Research Technician II, Laboratory of Sallie R. Permar, MD., Ph.D.

\begin{Detail}
\SubBulletItem
\textbf{\textit{Central Focus}}: My work focused on vaccine and non-vaccine strategies for the prevention and elimination of postnatal virus infections, with particular focus on HIV, CMV, and the Zika virus.
\SubBulletItem
Characterization of the determinants of interaction between Tenascin-C and the HIV-1 Env. \textit{Mangan et. al, Mucosal Immunology 2019}
\SubBulletItem
Assay development for the characterization of the HIV-1 Env-specific B cell repertoire by next-generation sequencing of immunoglobulin heavy chains from Env-vaccinated rhesus macaques.
\SubBulletItem
Functional characterization of the vaccine elicited antibody repertoire in Env-vaccinated infant rhesus macaques by antigen-specific B cell sorting, monoclonal antibody generation, and ELISA epitope mapping.
\SubBulletItem
Elicitation of widened neutralization breadth in SHIV-infected rhesus macaques as a potential protective strategy against mother to child transmission. 
\end{Detail}

\BigGap
\Entry
\href{https://www.davidson.edu/academic-departments/biology}
{\textbf{Davidson College Biology Department}},
Davidson, North Carolina \hfill
\DatestampYMD{2015}{08}{15} --
\DatestampYMD{2015}{012}{15}
\Gap
\BulletItem
Student Research Assistant, Laboratory of Rachid El Bejjani, Ph.D.
\begin{Detail}
\SubBulletItem
\textbf{\textit{Central Focus}}: My work identified and characterized a novel function of \textit{Rab-6.2} in cuticle development and skin permeability in \textit{Caenorhabditis elegans}.
\end{Detail}

\BigGap
\Entry
\href{https://cancer.uillinois.edu/member/paul-grippo/}
{\textbf{Department of Medicine, University of Illinois at Chicago}},
Chicago, Illinois \hfill
\DatestampYMD{2015}{05}{15} --
\DatestampYMD{2015}{08}{15}
\Entry
\textbf{Feinberg School of Medicine, Northwestern University},
Chicago, Illinois \hfill
\DatestampYMD{2012}{05}{15} --
\DatestampYMD{2014}{08}{15}
\Gap
\BulletItem
Summer Research Intern, Laboratory of Paul Grippo, Ph.D.
\begin{Detail}
\SubBulletItem
\textbf{\textit{Central Focus}}: My work focused on signaling in the tumor microenvironment of colorectal cancer and pancreatic ductal adenocarcinoma. 
\SubBulletItem
I evaluated the role of TGF-β in fibrosis, immune evasion, and PDAC tumorigenesis. 
\SubBulletItem
I investigated the tumor suppressive mechanisms of pigment epithelium-derived factor (PEDF) in pancreatic tumor progression.
\SubBulletItem
I investigated the mechanism of high ω-6 fatty acid diets to pancreatic tumor susceptibility.
\end{Detail}

\pagebreak

%%%%%%%%%%%%%%%%%%
%% PUBLICATIONS %%
%%%%%%%%%%%%%%%%%%

\Section
{Publications}
{Publications}
{PDF:Publications}

\BigGap
\SubSection
{14 Total, 1 as First Author}
{14 Total, 1 as First Author}
{PDF:14 Total, 1 as First Author}

% Declare a new group to limit the scope of \MaxNumberedItem to this subsection.
\begingroup
\renewcommand{\MaxNumberedItem}{[88]}
\BigGap
Berendam S*, Morgan-Asiedue PK*, \textbf{Mangan RJ}, Li S, Heimsath H, Luo K, Curtis A, Eudailey J, Faison W, Fox C, Phillips B, Tomai M, Kunz E, Itell H, Hudgens M, Cronin K, Wiehe K, Alam SM, Van Rompay KKA, De Paris K, Permar SR, Moody MA, Fouda GG. (2021)  Different adjuvanted pediatric HIV envelope vaccines induced distinct plasma antibody responses despite similar B cell receptor repertoires in infant rhesus macaques. \textbf{\textitf{PLOS One}} (Accepted). *Indicates co-first author.
\Gap
Nelson AN, Dennis M, Mangold JF, Li K, Saha PT, Cronin K, Kumar A, \textbf{Mangan RJ}, Shaw GM, Bar K, Haynes B, Moody MA, Alam M, Pollara J, Hudgens MG, Van Rompay KKA, De Paris K, Permar SR. (2021) Leveraging antigenic seniority for maternal vaccination to prevent mother-to-child transmission of HIV-1. \textbf{\textit{Under Review (NPJ Vaccines)}}.
\Gap
\Gap
Itell HL, Berenz A, \textbf{Mangan RJ}, Permar SR, Kaufman D. (2020) Systemic and mucosal levels of lactoferrin in very low birth weight infants supplemented with bovine lactoferrin. \textbf{\textit{Biochemistry and Cell Biology.}} https://doi.org/10.1139/bcb-2020-0238.
\Gap
Martinez DR, Tu JJ, Kumar A, Mangold JF, \textbf{Mangan RJ}, Goswami R, Giorgi EE, Chen J, Mengual M, Douglas AO, Heimsath H, Saunders KO, Nicely NI, Eudailey J, Hernandez G, Morgan-Asiedu PK, Wiehe K, Haynes BF, Moody MA, LaBranche C, Montefiori DC, Gao F, Permar SR. (2019) Maternal broadly neutralizing responses select for neutralization-resistant infant transmitted/founder HIV variants. \textbf{\textit{mBio.}} 10.1128/mBio.00176-20.
\Gap
Goswami R, Nelson AN, Tu JJ, Dennis M, Feng L, Kumar A, Mangold J, \textbf{Mangan RJ}, Mattingly C, Curtis AD, Obregon-Perko V, Mavigner M, Pollara J, Shaw GM, Bar K, Chahroudi A, De Paris K, Chan C, Van Rompay KKA, Permar SR. (2019) Analytical treatment interruption of postnatal SHIV infection after short-term anti-retroviral therapy in an infant rhesus macaque model. \textbf{\textit{mBio.}} 10(5): e01971-19.
\Gap
Nelson AN, Goswami R, Dennis M, Tu J, \textbf{Mangan RJ}, Saha P, Cain DW, Shen X, Bar K, Hudgens M, Pollara J, De Paris K, Van Rompay KKA, and Permar SR. (2019) SHIV CH505 infected infant and adult rhesus macaques exhibit similar HIV Env-specific antibody kinetics, despite distinct T follicular helper (Tfh) and germinal center B cell landscapes. \textbf{\textit{Journal of Virology.}} 93(15): e00168-19.
\Gap
\textbf{Mangan RJ}, Stamper L, Ohashi T, Eudailey JA, Go EP, Jeager F, Itell HL, Watts BE, Fouda GG, Erickson HP, Alam SM, Desaire H, Permar SR. (2019) Determinants of tenascin-C and HIV Env binding and neutralization. \textbf{\textit{Mucosal Immunology}}. 12: 1004-1012.
\Gap
Kim J*, Chun A*, \textbf{Mangan RJ}, Doyle H, Mourao B, and El Bejjani R. (2019) A retromer-independent function for RAB-6.2/RAB6 in C. elegans epidermis integrity. \textbf{\textit{Journal of Cell Science}}. 8(3): 3826-2839. *Indicates co-first author.
\Gap
Himes JE, Goswami R*, \textbf{Mangan RJ*}, Kumar A, Jeffries TL, Eudailey JA, Hemsath H, Nguyen QN, Pollara J, LaBranche C, Chen M, Vandergrift NA, Schiro F, Midkiff C, Ferrari G, Montefiori DC, Alvarez-Hernandez X, Aye PP, Permar SR. (2018) Polyclonal anti-HIV envelope breast milk antibodies limit founder SHIV acquisition and cell-associated virus loads in infant rhesus monkeys. \textit{\textbf{Mucosal Immunology.}} 11(6): 1716-1726. \textit{\textbf{*Co-second author.}}
\Gap
Nguyen QN, Martinez DR, Himes JE, Edwards RW, Han Q, Kumar A, \textbf{Mangan R}, Nicely NI, Shen X, Pollara J, Permar SR. (2018) Predominant envelope variable loop 2-specific and antibody-dependent cellular cytotoxicity antibody responses in acutely SIV-infected African green monkeys. \textbf{Retrovirology}. 15(1): 24. 
\Gap
Principe DR, Diaz AM, Torres C, \textbf{Mangan RJ}, DeCant B, McKinney R, Tsao MS, Lowy A, Munshi HG, Grippo PJ. (2017) TGFβ engages MEK/ERK to differentially regulate benign and malignant pancreas cell function. \textbf{\textit{Oncogene}}. 36(30):4336-4348.
\Gap
Principe DR, \textbf{Mangan RJ}, Grippo PJ. (2017) Transforming Growth Factor β. \textit{\textbf{Cancer Therapeutic Targets}}, pp.503-516. (Textbook Chapter)
\Gap
Principe DR, DeCant B, Staudacher J, Vitello D, \textbf{Mangan RJ}, Wayne E, Mascariñas E, Diaz AM, Bauer J, McKinney RD, Khazaie K, Pasche B, Dawson DW, Munshi HG, Grippo PJ, Jung B. (2016) Loss of TGFβ signaling promotes colon cancer progression and tumor-associated inflammation. \textbf{\textit{Oncotarget}}. 8(3):3826-3839. 
\Gap
Principe DR, Decant B, Diaz AM, \textbf{Mangan RJ}, Hwang R, Lowy A, Shetuni BB, Sreekumar BK, Chung C, Bentrem DJ, Munshi HG, Jung B, Grippo PJ, Bishehsari F. (2016) PEDF inhibits pancreatic tumorigenesis by attenuating the fibroinflammatory reaction. \textbf{\textit{Oncotarget}}. 7(19): 28218-28234.


\href{http://www.example.com/my-paper-doi-4}


\endgroup

%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Presentations %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%

\Section
{Presentations}
{Presentations}
{PDF:Presentations}

\SubSection
{Poster Presentations}
{Poster Presentations}
{PDF: Poster Presentations}

\Gap
\Entry
2019 Duke University Division of Human Genetics Retreat
\Gap
\Entry
2017 and 2018 Duke University Department of Pediatrics Research Retreat
\Gap
\Entry
2016, 2017, and 2018 Center for AIDS Research (CFAR) Retreat, Duke University
\Gap
\Entry
2016 Math and Science Research Symposium, Davidson College Biology Department
\Gap
\Entry
2016 Community-Based Learning Poster Session, Davidson College Department of Mathematics and Computer Science
\BigGap

\SubSection
{Invited Talks}
{Invited Talks}
{PDF: Invited Talks}

\Gap
\Entry
2020 Duke University Division of Human Genetics Retreat. \textit{\textbf{“High-throughput functional analysis of the fastest evolving regions of the human genome.”}}
\Gap
\Entry
2019 Duke University Department of Molecular Genetics and Microbiology Research Retreat. \textit{\textbf{“Exploring the fastest evolving regions of the human genome.”}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% AWARDS & SCHOLARSHIPS %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%

\Section
{Awards \&\newline
Scholarships}
{Awards \& Scholarships}
{PDF:AwardsAndScholarships}

\BulletItem
Triangle Center for Evolutionary Medicine Graduate Student Award
\hfill
\DatestampY{Fall 2020}

\BulletItem
Sigma Xi Grants-In-Aid of Research.
\hfill
\DatestampY{2019}
\begin{Detail}
\Item
Matching contribution from the Duke Graduate School.
\end{Detail}

\Gap
\BulletItem
Steinway Piano Gallery-Charlotte Award 
\hfill
\DatestampYM{2016}{05}
\begin{Detail}
\Item
For pianistic excellence and academic achievement.\\
2016 Davidson College Honoree.
\end{Detail}

\Gap
\BulletItem
Donald B. Plott and J. Estes Millner Scholarship, Davidson College
\hfill
\DatestampY{2012}--\DatestampY{2016}
\begin{Detail}
\Item
For students with exceptional talent and passion for music.
\end{Detail}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% RESEARCH SKILLS %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\Section
{Research Skills}
{Research Skills}
{PDF: Research Skills}
\BulletItem
Software Engineering\\
Co-author of Gonomics, an open-source genomics software platform for the Go programming language. Specific expertise 
in bioinformatic software development for data analysis for comparative genomics, population genomics, and next-generation 
sequencing. Previous experience writing in the R, Python, Java, and Go programming languages. Extensive experience
with Adobe Illustrator, GraphPad Prism, Microsoft Office, FlowJo, ImageJ, and {\LaTeX}. Proficiency in front-end web 
development in HTML and CSS.
\BulletItem
Animal Research\\
Mouse handling and husbandry, genotyping, survival surgery, behavior, tissue resection, and perfusion. 
Human and non-human primate blood and tissue sample processing. \itemit{C. elegans} colony maintenance, 
Mendelian genetics, behavioral and pharmacological assays. \\
\BulletItem
Molecular Biology\\
Western blotting, immunoprecipitation, histology, flow cytometry, ELISA, cell culture, plasmid production and cloning, 
monoclonal antibody production, next-generation sequencing, confocal and super-resolution microscopy.\\

%%%%%%%%%%%%%%%%%%%%%%%
%% CAMPUS ACTIVITIES %%
%%%%%%%%%%%%%%%%%%%%%%%

\Section
{Other Information}
{Other Information}
{PDF: Other Information}

\Gap
\BulletItem
Freelance Jazz Piano \hfill{\DatestampY{2011}-- Present}
\begin{Detail}
\SubBulletItem
Part-time working jazz pianist and composer in the Chicago, IL and Durham, NC areas. 
\SubBulletItem
Featured on the National Public Radio program "Says You" in November, 2013. 
\SubBulletItem
Performed in venues including the Smithsonian National Museum of African American History and Culture, the Cadillac Palace Theatre, the Civic Opera House, the Durham Performing Arts Center, and on the Royal Caribbean \textit{Vision of the Seas}.
\SubBulletItem
Regular performer with Grammy-nominated jazz artist John Brown. Shared the stage with numerous jazz luminaries including Delfaeyo Marsalis, Grace Kelly, Christian Sands, Wayne Bergeron, and Wycliffe Gordon.
\SubBulletItem
First solo studio album “Christmas!” released on Soundcloud.com in December 2017. 
\end{Detail}
\Gap
\BulletItem
French Language - Intermediate proficiency for reading, writing, and speaking.

%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% OTHER WORK EXPERIENCE %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\Section
%{Other Work\newline
%Experience}
%{Other Work Experience}
%{PDF:OtherWorkExperience}

%\Entry
%\href{http://www.example.com/my-company}
%{\textbf{Alpha Engineering Firm}},
%Oakland, Ohio, USA

%\Gap
%\BulletItem
%Project Officer,
%Department of Meteorological Sciences,
%\hfill
%\DatestampYMD{2007}{10}{15} --
%\DatestampYMD{2008}{01}{15}
%\newline
%Research \& Development Division
%\begin{Detail}
%\SubBulletItem
%Nullam venenatis egestas nisl eget elementum.
%\SubBulletItem
%Nulla finibus justo vel turpis efficitur, non lacinia orci maximus. Proin rhoncus, felis vel hendrerit lacinia, enim ipsum ultricies massa, sit amet interdum nisi massa sit amet justo.
%\SubBulletItem
%Etiam vitae eros mollis, consectetur quam quis, molestie massa.
%\end{Detail}

%%%%%%%%%%%%%%%
%% LANGUAGES %%
%%%%%%%%%%%%%%%

%\Section
%{Languages}
%{Languages}
%{PDF:Languages}
%
%\BulletItem
%English: Native language.
%
%\Gap
%\BulletItem
%Spanish: Fluent (speaking, reading, writing).
%
%\Gap
%\BulletItem
%Latin: Intermediate (reading); basic (speaking, writing).

%%%%%%%%%%%%%%%
%% INTERESTS %%
%%%%%%%%%%%%%%%

%\Section
%{Interests}
%{Interests}
%{PDF:Interests}
%
%\Entry
%Digital photography,
%typography,
%swimming.

%%%%%%%%%%%%%%%%
%% REFERENCES %%
%%%%%%%%%%%%%%%%

%
%\Section
%{References}
%{References}
%{PDF:References}
%
%\BulletItem
%\textbf{Craig B. Lowe, Ph.D.}
%\newline
%Assistant Professor of Molecular Genetics and Microbiology
%\newline
%Duke University
%\newline
%Box 3175, Durham, NC 27710
%\newline
%\href{mailto:craig.lowe@duke.edu}
%{craig.lowe@duke.edu}
%\,\SubBulletSymbol\,
%+1\,(919)\,613-1754
%
%\BigGap
%\BulletItem
%\textbf{Sallie R. Permar, MD., Ph.D.}
%\newline
%Professor of Pediatrics, Molecular Genetics and Microbiology, and Immunology
%\newline
%Associate Dean of Physician Scientist Development
%\newline
%Duke Human Vaccine Institute, Duke University Medical Center
%\newline
%Box 103020, Durham, NC 27710
%\newline
%\href{mailto:sallie.permar@duke.edu}
%{sallie.permar@duke.edu}
%\,\SubBulletSymbol\,
%+1\,(919)\,684-2515
%
%
%\BigGap
%\BulletItem
%\textbf{Rachid El Bejjani, Ph.D.}
%\newline
%Assistant Professor
%\newline
%Biology Department, Davidson College
%\newline
%Box 7118, Davidson, NC 28035
%\newline
%\href{mailto:raelbejjani@davidson.edu}
%{raelbejjani@davidson.edu}
%\,\SubBulletSymbol\,
%+1\,(704)\,894-2603

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% MULTILINGUAL UNICODE EXAMPLES %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\Section
%{Multilingual Unicode Examples}
%{Multilingual Unicode Examples}
%{PDF:MultilingualUnicodeExamples}
%
%\BulletItem
%Assortment of unicode characters from
%\href{http://www.ltg.ed.ac.uk/~richard/unicode-sample.html}
%{\url{http://www.ltg.ed.ac.uk/~richard/unicode-sample.html}}
%
%\begin{Detail}
%\Item
%\textbf{Latin Extended-A}
%Ā ā Ă ă Ą ą Ć ć Ĉ ĉ Ċ ċ Č č Ď ď Đ đ Ē ē Ĕ ĕ Ė ė Ę ę Ě ě Ĝ ĝ Ğ ğ Ġ ġ Ģ ģ Ĥ ĥ Ħ ħ Ĩ ĩ Ī ī Ĭ ĭ Į į İ ı Ĳ ĳ Ĵ ĵ
%\textbf{Latin Extended-B}
%ƀ Ɓ Ƃ ƃ Ƅ ƅ Ɔ Ƈ ƈ Ɖ Ɗ Ƌ ƌ ƍ Ǝ Ə Ɛ Ƒ ƒ Ɠ Ɣ ƕ Ɩ Ɨ Ƙ ƙ ƚ ƛ Ɯ Ɲ ƞ Ɵ Ơ ơ Ƣ ƣ Ƥ ƥ Ʀ Ƨ ƨ Ʃ ƪ ƫ Ƭ ƭ Ʈ Ư ư Ʊ Ʋ Ƴ ƴ Ƶ
%\textbf{Latin Extended Additional}
%Ḁ ḁ Ḃ ḃ Ḅ ḅ Ḇ ḇ Ḉ ḉ Ḋ ḋ Ḍ ḍ Ḏ ḏ Ḑ ḑ Ḓ ḓ Ḕ ḕ Ḗ ḗ Ḙ ḙ Ḛ ḛ Ḝ ḝ Ḟ ḟ Ḡ ḡ Ḣ ḣ Ḥ ḥ Ḧ ḧ Ḩ ḩ Ḫ ḫ Ḭ ḭ Ḯ ḯ Ḱ ḱ Ḳ ḳ Ḵ ḵ
%\textbf{Greek}
%ʹ ͵ ͺ ; ΄ ΅ Ά · Έ Ή Ί Ό Ύ Ώ ΐ Α Β Γ Δ Ε Ζ Η Θ Ι Κ Λ Μ Ν Ξ Ο Π Ρ Σ Τ Υ Φ Χ Ψ Ω Ϊ Ϋ ά έ ή ί ΰ α β γ δ ε ζ η θ
%\textbf{Cyrillic}
%Ё Ђ Ѓ Є Ѕ І Ї Ј Љ Њ Ћ Ќ Ў Џ А Б В Г Д Е Ж З И Й К Л М Н О П Р С Т У Ф Х Ц Ч Ш Щ Ъ Ы Ь Э Ю Я а б в г д е ж з
%\textbf{Hebrew}
%א ב ג ד ה ו ז ח ט י ך כ ל ם מ ן נ ס ע ף פ ץ צ ק ר ש ת װ ױ ײ ֝ ֞ ֟ ֠ ֡ ֣ ֤ ֥ ֦ ֧ ֨ ֩ ֪ ֫ ֬ ֭ ֮ ֯ ְ ֱ ֒ ֓ ֔
%\textbf{Armenian}
%{\UseSecondaryFont
%Ա Բ Գ Դ Ե Զ Է Ը Թ Ժ Ի Լ Խ Ծ Կ Հ Ձ Ղ Ճ Մ Յ Ն Շ Ո Չ Պ Ջ Ռ Ս Վ Տ Ր Ց Ւ Փ Ք Օ Ֆ ՙ ՚ ՛ ՜ ՝ ՞ ՟ ա բ գ դ ե զ}
%\textbf{Thai}
%{\UseSecondaryFont
%ก ข ฃ ค ฅ ฆ ง จ ฉ ช ซ ฌ ญ ฎ ฏ ฐ ฑ ฒ ณ ด ต ถ ท ธ น บ ป ผ ฝ พ ฟ ภ ม ย ร ฤ ล ฦ ว ศ ษ ส ห ฬ อ ฮ ฯ ะ ั า ำ ิ}
%\end{Detail}

% Manual page break.
%\newpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% THIS IS A SECTION WITH USAGE NOTES %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%% Declare a new group to limit the scope of \color to this section.
%\begingroup
%\color{blue}
%
%\Section
%{This is a\newline
%Section\newline
%With\newline
%Usage Notes}
%{This is a Section With Usage Notes (For PDF Bookmark)}
%{PDF:ThisIsASectionWithUsageNotes:ForPDFLink}
%
%\SubSection
%{This is a SubSection}
%{This is a SubSection (For PDF Bookmark)}
%{PDF:ThisIsASubSection:ForPDFLink}
%
%\BigGap
%\BulletItem
%Use \CodeCommand{Section\{a\}\{b\}\{c\}} and
%\CodeCommand{SubSection\{a\}\{b\}\{c\}}
%to create sections and subsections, where
%\Code{a} is the heading displayed on the page,
%\Code{b} is the PDF bookmark heading, and
%\Code{c} is the internal PDF link (must be unique).
%Sections and subsections will appear in the PDF bookmarks.
%Note the CamelCase command names.
%
%\Gap
%\BulletItem
%Use
%\CodeCommand{Entry},
%\CodeCommand{BulletItem},
%\CodeCommand{SubBulletItem},
%\CodeCommand{SubSubBulletItem},
%\CodeCommand{Item},
%\CodeCommand{SubItem},
%\CodeCommand{SubSubItem},
%\CodeCommand{NumberedItem},
%etc.,
%to create entries in the main body of the CV.
%
%\Gap
%\BulletItem
%Enclose entry details between
%\CodeCommand{begin\{Detail\}} and
%\CodeCommand{end\{Detail\}}
%so that they are typeset in a smaller font.
%\begin{Detail}
%\Item
%This is an example of entry detail text enclosed in a \Code{Detail} environment.
%\end{Detail}
%
%\Gap
%\BulletItem
%Use \CodeCommand{Gap} and \CodeCommand{BigGap} to insert vertical spaces between entries to improve layout.
%
%\BigGap
%\SubSection
%{This is Another SubSection}
%{This is Another Subsection (For PDF Bookmark)}
%{PDF:ThisIsAnotherSubSection:ForPDFLink}
%
%\BigGap
%\Entry
%This is a plain \CodeCommand{Entry},
%followed by an \CodeCommand{hfill} and a date range
%\hfill
%\DatestampYM{2015}{10} --
%\DatestampYM{2015}{12}
%
%\Gap
%\BulletItem
%This is a \CodeCommand{BulletItem}.
%\Item
%This is an \CodeCommand{Item}, which has no bullet.
%Note the alignment with the \CodeCommand{BulletItem} above.
%
%\Gap
%\SubBulletItem
%This is a \CodeCommand{SubBulletItem}.
%\SubItem
%This is a \CodeCommand{SubItem}, which has no bullet.
%Note the alignment with the \CodeCommand{SubBulletItem} above.
%
%\Gap
%\SubSubBulletItem
%This is a \CodeCommand{SubSubBulletItem}.
%\SubSubItem
%This is a \CodeCommand{SubSubItem}, which has no bullet.
%Note the alignment with the \CodeCommand{SubSubBulletItem} above.
%
%\Gap
%\NumberedItem{[42]}
%This is a \CodeCommand{NumberedItem}.
%Change the value of the macro \CodeCommand{MaxNumberedItem} to adjust the indentation width.
%
%\BigGap
%\SubSection
%{Line, Paragraph, and Page Breaks}
%{Line, Paragraph, and Page Breaks (For PDF Bookmark)}
%{PDF:LineParagraphAndPageBreaks:ForPDFLink}
%
%\BigGap
%\BulletItem
%To create a new line within the same paragraph (i.e., preserving the same paragraph indentation), use \CodeCommand{newline} instead of \CodeCommand{\textbackslash};
%the latter will reset the paragraph indentation.
%
%\Gap
%\BulletItem
%To create a new paragraph, use \CodeCommand{par} or simply leave an empty line.
%Paragraph indentations (from
%\CodeCommand{Entry},
%\CodeCommand{BulletItem},
%\CodeCommand{SubBulletItem},
%\CodeCommand{SubSubBulletItem},
%\CodeCommand{Item},
%\CodeCommand{SubItem},
%\CodeCommand{SubSubItem},
%\CodeCommand{NumberedItem},
%etc.) do not carry across different paragraphs.
%
%\Gap
%\BulletItem
%To create a new page, use \CodeCommand{newpage}.
%
%\BigGap
%\SubSection
%{Dates}
%{Dates (For PDF Bookmark)}
%{PDF:Dates:ForPDFLink}
%
%\BigGap
%\BulletItem
%Use the following macros to specify and display dates consistently:
%\SubBulletItem
%\CodeCommand{DatestampYMD\{yyyy\}\{MM\}\{dd\}}
%(e.g., \CodeCommand{DatestampYMD\{2008\}\{01\}\{15\}})
%\SubBulletItem
%\CodeCommand{DatestampYM\{yyyy\}\{MM\}}
%(e.g., \CodeCommand{DatestampYM\{2008\}\{01\}})
%\SubBulletItem
%\CodeCommand{DatestampY\{yyyy\}}
%(e.g., \CodeCommand{DatestampY\{2008\}})
%
%\Gap
%\BulletItem
%Change the date format option passed to the document class to adjust how dates are displayed throughout the document:
%\SubBulletItem
%\Code{MMMyyyy} (``Jan~2008'')
%\SubBulletItem
%\Code{ddMMMyyyy} (``15~Jan~2008'')
%\SubBulletItem
%\Code{MMMMyyyy} (``January~2008'')
%\SubBulletItem
%\Code{ddMMMMyyyy} (``15~January~2008'')
%\SubBulletItem
%\Code{yyyyMMdd} (``2008-01-15'')
%\SubBulletItem
%\Code{yyyyMM} (``2008-01'')
%\SubBulletItem
%\Code{yyyy} (``2008'')
%
%\endgroup
%
\end{Body}
%
%%%%%%%%%%%%
%% CV NOTE %
%%%%%%%%%%%%

\UseNoteFont%
%\null\hfill
%[\textit{\CVNote}]

\end{document}
